A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-02-08 paper/paper.Rmd
extending conclusions

- determining which records should be downloaded from the database.
- there are many errors in the data, e.g. hourly wages greater than $30,000 per hour.
- there is no explicit variable in the database recording high school dropout, which means we needed to compare date of 12th grade with the individual's age.
- calculating experience in the workforce would require knowing the time of first job within the first year the individual was recorded.

@@

>>>>

- determining which records should be downloaded from the database.
- there are many errors in the data, e.g. hourly wages greater than $30,000 per hour.
- there is no explicit variable in the database recording high school dropout, which means we needed to compare the date of 12th grade with the individual's age.
<!-- calculating experience in the workforce would require knowing the time of first job within the first year the individual was recorded.-->

@@

Why is this exercise important for teachers and students? The data package and software could be used for illustrating data cleaning in the classroom. The data provided in the package can be used as examples i nthe teaching of initial data analysis, and modeling, and exploratory data analysis of longitudinal data.

XXX Importance of public policy vs for the public; and the importance of using relatable data examples in teaching that it needs to be acurate, and limitations on interpretation need to be available.

### 2022-02-08 paper/paper.tex
extending conclusions

\begin{itemize}
\tightlist
\item
  determining which records should be downloaded from the database.
\item
  there are many errors in the data, e.g.~hourly wages greater than \$30,000 per hour.
\item
  there is no explicit variable in the database recording high school dropout, which means we needed to compare date of 12th grade with the individual's age.
\item
  calculating experience in the workforce would require knowing the time of first job within the first year the individual was recorded.
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  determining which records should be downloaded from the database.
\item
  there are many errors in the data, e.g.~hourly wages greater than \$30,000 per hour.
\item
  there is no explicit variable in the database recording high school dropout, which means we needed to compare the date of 12th grade with the individual's age.
\end{itemize}
